Word Sense Disambiguation: Pipelining with Supervised LSA

### 2014-05-11 paper.tex

        One widely used knowledge-based algorithm is Lesk's algorithm.  Given that there are two words W1 and W2 with multiple word senses.
	for each sense i in W1
	   for each sense j in W2
	      calculate overlap of i and j in dictionary definitions
	Maximize overlap i and j to determine the respective word senses of W1 and W2.
	Semantic similarity:
	calculate path between words in wordnet for each word sense with other words in the context
	minimize total semantic path to select word sense
	context can vary from one sentence to length of document

>>>>

        One widely used knowledge-based algorithm is Lesk's algorithm.  Given that there are two words W1 and W2 with multiple word senses.
	for each sense i in W1
	   for each sense j in W2
	      calculate overlap of i and j in dictionary definitions
	Maximize overlap i and j to determine the respective word senses of W1 and W2.

        Another knowledge-based algorithm is semantic similarity.  In order to calculate semantic similarity, calculate path between words in Wordnet for each possible word sense of the ambiguous word with other words in the context.  To select the correct word sense, minimize the total semantic path.  The context of the word depends, and can vary from one sentence to the length of the document.  Generally, only nouns are used to provide context.
